Appendix S1: Supporting Information

### 2021-09-07 ms/SI.Rmd
Make binary trait sig table long

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  # format for kable/latex
  mutate(trait = str_replace_all(trait, "_", "\\\\_")) %>%
  rename(
    "Trait" = trait,
    `\\textit{N} present` = num_present,
    `\\textit{N} absent` = num_absent,
    `\\textit{D}` = D,
    `\\textit{P}(random)` = prob_random, 
    `\\textit{P}(Brownian)` = prob_brownian
  ) %>%
  kbl(booktabs = TRUE, escape = FALSE, format = "latex") %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position"))
```

>>>>

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  # format for kable/latex
  mutate(trait = str_replace_all(trait, "_", "\\\\_")) %>%
  rename(
    "Trait" = trait,
    `\\textit{N} present` = num_present,
    `\\textit{N} absent` = num_absent,
    `\\textit{D}` = D,
    `\\textit{P}(random)` = prob_random, 
    `\\textit{P}(Brownian)` = prob_brownian
  ) %>%
  kbl(booktabs = TRUE, escape = FALSE, format = "latex", longtable = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position", "repeat_header"))
```
